% !TEX root = ../main.tex
%
\chapter{Introduction}
\label{sec:intro}

main intro part, in general it should contain at least 4 paragraphs each answers one of the following questions.

\emph{P1: What's the thesis main problem?}

\emph{P2: Why the problem is a problem?}

\emph{P3: what's the solution?}

\emph{P4: Why the solution is better than the state of the art?}

\section{Overview}
\label{sec:intro:overview}

In the first part of this thesis,
we explore ...

In the second part of the thesis,
we present \system{},
a ...
To answer this challenge, \system{} takes a hybrid approach, and
...

To address the requirements of ..., \system{}
enables ...

Finally, this thesis addresses a number of design and implementation
challenges, including ...

\section{Contributions}
\label{sec:intro:contributions}

The main results of this dissertation are as follows:
\begin{itemize}[leftmargin=*]
\item
  R1
\item
  R2
\item
  R3
\item
  R4
\item
  R5
\end{itemize}

Our experimental evaluation shows that:...

\section{Publications}
\label{sec:intro:publications}

Some of the results presented in this thesis have been published as follows:

\begin{itemize}
  \item myFirstPublication %\cite{toumlilt:hal-03353663}
  \item mySecondPublication %\cite{toumlilt:hal-01860334}
\end{itemize}

During my thesis, I explored other directions and collaborated in several projects that have helped me to get insights on the challenges of ... These efforts have led me to contribute to the following publications and deliverables:

\begin{itemize}
  \item TechReport %\cite{LiRAv09p46:online}
  \item ANRProjectDelivrable %\cite{D61Newco32:online}
  \item EUProjectDelivrable %\cite{D62Newco60:online}
\end{itemize}

\section{Organization}
\label{sec:intro:organisation}

This thesis is divided into three parts. 
The rest of this document is organized as follows:
\begin{itemize}
  \item Part~\ref{part:background} introduces the common background of our work,
  formulate the problem, presents the existing solutions and discusses the use-case
  requirements, this part is divided into three chapters:
  \begin{itemize}
    \item Chapter~\ref{ch:my-domain} provides a complete and up-to-date 
    review of the MyDomain.
    \item Chapter~\ref{ch:requirements} presents a use-case point of view of the
    ...
    \item Chapter~\ref{ch:related-work} studies and compares the solutions that have
    been designed in the state of the art of ...
  \end{itemize}
  \item Part~\ref{part:contributions}, in light of what we saw in the existing work, 
  we will here justify some protocol choices used in our approach...
  \item Part~\ref{part:evaluation} provides an experimental evaluation 
  demonstrating the benefits of our approach, compared to other solutions 
  from the state of the art.
  \item the last part~\ref{part:conclusion} we summarize our contribution, and 
  present our vision for the future requirements towards more ...
\end{itemize}
